\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-25 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex
Travail collectif
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Vessel: Transport costs estimates, selected years, 4-digit level}
		\label{tab:result_air_rob}%
		\input{TableB1_ves_reshaped.tex}
		\begin{tablenotes}
			\scriptsize
			\item Statistics are obtained weighting each observation by its share in trade (mode-dependent).
			\item \textbf{Model (A): Ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\end{tablenotes}
\end{table}

@@

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Vessel: Measures of goodness of fit, 4-digit level}
		\label{tab:good_fit_air_rob}%
		\input{TableB3_ves_reshaped.tex}
		%\begin{tablenotes}
{\parbox[l]{12cm}{
			\scriptsize{ Notes: Model (A) = with only ad-valorem transport costs. Model (B) = with additive \& ad-valorem transport costs. $R^{2}$ between the log of predicted ratio and the log of the observed ratio. The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of sectors. }}}
		%\end{tablenotes}
	\end{table}

@@

\paragraph{Estimation issue} Getting deeper on the estimated functional form raised another difficulty in adapting our equation to per-unit rather than per-weight price. As discussed above, in our baseline regression we separate each transport cost component in two distinct sector-country dimensions. As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector. In the specific case of quantities, this raises a non-trivial issue for country-level fixed effects. Sector-level fixed effects could indeed be easily replaced by (sector times quantity unit) fixed effects; but the same does not appear possible for country fixed effects. Let us elaborate on this issue.

>>>>

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Vessel: Transport costs estimates, selected years, 4-digit level}
		\label{tab:result_ves_rob}%
		\input{TableB1_ves_reshaped.tex}
		\begin{tablenotes}
			\scriptsize
			\item Statistics are obtained weighting each observation by its share in trade (mode-dependent).
			\item \textbf{Model (A): Ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\end{tablenotes}
\end{table}

@@

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Vessel: Measures of goodness of fit, 4-digit level}
		\label{tab:good_fit_ves_rob}%
		\input{TableB3_ves_reshaped.tex}
		%\begin{tablenotes}
{\parbox[l]{12cm}{
			\scriptsize{ Notes: Model (A) = with only ad-valorem transport costs. Model (B) = with additive \& ad-valorem transport costs. $R^{2}$ between the log of predicted ratio and the log of the observed ratio. The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of sectors. }}}
		%\end{tablenotes}
	\end{table}

@@

\paragraph{Estimation issue} Getting deeper on the estimated functional form raised another difficulty in adapting our equation to per-unit rather than per-weight price. As discussed above, in our baseline regression we separate each transport cost component in two distinct sector-country dimensions. As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector. In the specific case of quantities, this raises a non-trivial issue for country-level fixed effects. Sector-level fixed effects could indeed be easily replaced by (sector $\times$ quantity unit) fixed effects; but the same does not appear possible for country fixed effects. Let us elaborate on this issue.
